%! TEX program = xelatex
\documentclass[10pt]{article}

\usepackage{geometry}
\usepackage{enumitem}
\usepackage{fontspec}
\usepackage{xifthen}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage[none]{hyphenat}
\usepackage{fontawesome}

\usepackage[hidelinks]{hyperref}
\urlstyle{same} % style hyperlinks like regular text

\pagestyle{empty}
\geometry{margin=0.5in}
\setlength\parindent{0pt}
\setlist{nosep}
\setmainfont{Roboto-Light}
\setlength{\arrayrulewidth}{1.5pt}
\setlength{\tabcolsep}{10pt}

\newfontfamily\roboto{Roboto-Regular}
\newfontfamily\robotothin{Roboto-Thin}
\newcommand{\lmr}[1]{{\fontfamily{lmr}\selectfont#1}}

\newcommand{\name}[2]{
  \begin{minipage}{0.4\textwidth}
    \begin{flushright}
      \setlength{\tabcolsep}{0pt}
      \begin{tabular}{r}
        \fontsize{36pt}{0pt}\selectfont
        \MakeUppercase{#1 \textbf{#2}} \\
        \normalsize \, \textit{Software Engineer}\hfill \url{https://dav.sh/} \,
      \end{tabular}
    \end{flushright}
  \end{minipage}
}

\newcommand{\textlbf}[1]{{\roboto #1}}
\newcommand{\textlight}[1]{{\robotothin #1}}
\renewcommand{\date}[2]{#1 #2}
\newcommand{\daterange}[2]{#1 -- \ifthenelse{\equal{#2}{}}{\textit{Present}}{#2}}
\newcommand{\resumesection}[1]{\vspace{-0.2cm}\section*{#1}\vspace{-0.2cm}\vspace{0.1cm}}
\newcommand{\heading}[2]{\textbf{#1} \\ \textit{#2}}

\begin{document}

{
\setlength{\tabcolsep}{20pt}
\begin{center}
  \begin{tabular}{c | c}
% \name is self-explanatory. \topinfo is for things like social media, email, phone number, address, etc.
  \name{David}{Shen} & \begin{minipage}{0.4\textwidth}
    \vspace{6pt}
    \href{mailto:davi@d-shen.xyz}{davi@d-shen.xyz} \\
    \url{https://github.com/pantherman594} \\
    (617) 863-7436
    \vspace{6pt}
  \end{minipage}
\end{tabular}
\end{center}
}

\vspace{0.5cm}

\begin{minipage}[t]{0.25\textwidth}
  \begin{flushleft}
    \resumesection{Education}
    \textbf{Boston College} \newline
    \textit{B.S. in Computer Science} \newline
    \textlbf{GPA:} 3.93 \textlbf{Major GPA:} 3.97 \newline
    Dean's List First Honors. \newline
    \daterange{\date{Aug}{2018}}{\date{May}{2022}} \textit{\color{gray}{(exp.)}}

    \resumesection{Skills}
    \textbf{Languages} \newline
    C and C++ \newline
    TypeScript \newline
    Python \newline
    Rust \newline
    Go \newline
    Dart \newline
    Java \newline
    Bash \newline
    HTML + CSS

    \vspace{0.25cm}

    \textbf{Technologies} \newline
    Linux \newline
    Git \newline
    Node.js \newline
    React + Redux \newline
    Flutter \newline
    Express \newline
    NGINX \newline
    MongoDB \newline
    MariaDB \newline
    PostgreSQL

    \resumesection{Awards}
    \textbf{Codestellation} \newline
    Judge's Pick \newline
    \date{Nov 10}{2019}

    \vspace{0.15cm}

    Best Web/Mobile Hack \newline
    \date{Nov 4}{2018}

    \vspace{0.25cm}

    \textbf{Hack the Heights} \newline
    First Place \newline
    \date{Apr 14}{2019}

    \vspace{0.25cm}

    \textbf{Hack Haverhill} \newline
    First Place \newline
    \date{Nov 17}{2018}

    \vspace{0.25cm}

    \textbf{BC Hacks} \newline
    Grand Prize; Hacker's Choice \newline
    \date{Nov 11}{2018}
  \end{flushleft}
\end{minipage}
\hfill
\begin{minipage}[t]{0.7\textwidth}
  \begin{flushleft}

  \resumesection{Experience}
  \textbf{Microsoft} \, Base OS Kernel \hfill Redmond, WA \, \textbf{Remote} \newline
  \textit{Software Engineering Intern} \hfill \daterange{\date{Jun}{2020}}{\date{Aug}{2020}}
  \begin{itemize}
    \item Brought layering support, a feature highly desired by clients and other companies, to Windows Containers on Windows Desktop. This enables clients to create containers customized for their own purposes.
    \item Wrote a specification detailing the motivations behind and customer impact of the project.
  \end{itemize}

  \vspace{0.25cm}

  \textbf{Rocket Software} \, Zowe App Platform \hfill \textbf{Waltham, MA} \newline
  \textit{Software Engineering Intern} \hfill \daterange{\date{Jun}{2019}}{\date{Dec}{2019}}
  \begin{itemize}
    \item Built a new web interface for mainframes to filter and search for objects in a Db2 database, visualize and explore their hierarchical relationships, and define “Collections” of many objects.
    \item Designed and implemented a modular plugin system to add Microsoft Language Servers to a browser-based code editor for the mainframe.
  \end{itemize}

  \vspace{0.25cm}

  \textbf{Fellowship of Christian Clubs} \hfill \textbf{Remote} \newline
  \textit{Software Engineer} \hfill \daterange{\date{Jun}{2019}}{}
  \begin{itemize}
    \item Developed, maintained, and hosted the backend and database.
    \item Designed and helped develop the web interface.
  \end{itemize}

  \vspace{0.25cm}

  \textbf{Boston College} \hfill \textbf{Chestnut Hill, MA} \newline
  \textit{Teaching Assistant for Computer Science II} \hfill \daterange{\date{Jan}{2019}}{\date{May}{2019}}
  \begin{itemize}
    \item Wrote a script to automatically download students’ problem sets, suggest grades, and upload grades and comments to the Canvas Learning Management System, saving the professor hours of time.
    \item Assisted students with problem sets and answered student questions.
  \end{itemize}

  \vspace{0.25cm}

  \textbf{BC GET Delivery} \, \textit{\color{gray}{Student Run Startup}} \hfill \textbf{Chestnut Hill, MA} \newline
  \textit{Full Stack Developer} \hfill \daterange{\date{Oct}{2018}}{\date{Feb}{2019}}
  \begin{itemize}
    \item Developed an automated app-to-SMS messaging platform, to ease communication between deliverer and customer and improve customer privacy.
    \item Discovered and fixed critical security flaws.
  \end{itemize}

  \resumesection{Projects}

  \textbf{BC COVID-19 Dashboard} \hfill \href{https://bccovid.dav.sh/}{\faLink \, \textit{bccovid.dav.sh}} \quad \href{https://github.com/pantherman594/bc-covid}{\faGithub \, \textit{pantherman594/bc-covid}} \newline
  Unofficial COVID-19 dashboard to visualize the COVID-19 testing at Boston College during the 2021-22 school year. It automatically scrapes BC's official dashboard to display it in a more informative and user-friendly manner. Built with React and Recharts on the frontend, with a TypeScript backend and MongoDB database.

  \vspace{0.25cm}

  \textbf{In-Person Among Us} \newline
  Flutter app that recreates the Among Us game in real life, allowing players to complete tasks, kill nearby crewmates, and report bodies in real time. Tasks are initiated by scanning a QR code at a specified location, which launches the task in the app. The "wires" task was also recreated in real life with an Arduino.

  \vspace{0.25cm}

  \textbf{WikiWhere} \hfill \href{https://wikiwhere.ciliber.to/}{\faLink \, \textit{wikiwhere.ciliber.to}} \quad \href{https://github.com/wikiwhere/wikiwhere}{\faGithub \, \textit{wikiwhere/wikiwhere}} \newline
  Visualization of Wikipedia articles and their links. Built with d3 and Express.js, with a bi-directional breadth first search algorithm in C++.

  \vspace{0.25cm}

  \textbf{hackm.app} \hfill \href{https://hackmapp.dav.sh/}{\faLink \, \textit{hackmapp.dav.sh}} \quad \href{https://github.com/hackmapp/hackmapp}{\faGithub \, \textit{hackmapp/hackmapp}} \newline
  Interactive map of the previous, current, and upcoming MLH hackathons. Built with d3, Express.js, and BeautifulSoup.

  \end{flushleft}
\end{minipage}

\end{document}
